\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-21 doc/flexiblesusy-paper.tex
Minor corrections to paper

\subsection{Current limitations and future extensions}
Although we try to handle as many models as possible, there are still
some limitations to what can be done. In it's current form \fs assumes
all couplings are real, therefore it is limited to $CP$-conserving
versions of SUSY models.  Although it is implicit in the title, we
would like to stress that currently we cannot provide a spectrum
generator for non-SUSY models.  This also means that like other
spectrum generators it is difficult to reliably predict the mass
spectrum in extreme cases such as Split-SUSY
\cite{Wells:2003tf,ArkaniHamed:2004fb,Giudice:2004tc}, where the mass
scales of the SUSY model are drastically split, leading to very large
logarithms which are not resummed.  In such cases the tower of
effective theories offers the best possibility for a solution.
However, for this to work \fs must be extended to include non-SUSY
models.  Finally, the gauge group of the model is currently restricted
to be semi-simple and to contain the Standard Model gauge group as
factor, so that the SUSY model can be directly matched to the SM at
low energies.
%
Future releases which extend \fs beyond each of these limitations are
already planned.

@@

\fs allows the user to add leading two-loop contributions to the
$CP$-even and $CP$-odd Higgs self-energies as well as to the $CP$-even Higgs
tadpoles.  For MSSM-like models (with two $CP$-even Higgs bosons, one
$CP$-odd Higgs boson, one neutral Goldstone boson) routines dor
caluclating these corrections will be generated by setting
\code{UseHiggs2LoopMSSM = True} in the model file and by defining the
effective $\mu$-term \code{EffectiveMu = \\[Mu]}.  This will add the
zero-momentum corrections of the order $O(y_t^4 + y_b^2 y_t^2 +
y_b^4)$, $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$, $O(y_\tau^4)$ from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}.
For NMSSM-like models (with three $CP$-even Higgs bosons, two $CP$-odd
Higgs bosons, one neutral Goldstone boson) the two-loop contributions
are generated by setting \code{UseHiggs2LoopNMSSM = True} and by
defining the effective $\mu$-term like \code{EffectiveMu = \\[Lambda]
  vS / Sqrt[2]}, for example.  This will add the zero-momentum
corrections of the order $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ from
\cite{Degrassi:2009yq} and also the MSSM contributions of the order
$O(y_\tau^4)$, $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ as well
\cite{Brignole:2001jy,Dedes:2003km} which only represent a partial
correction for that order in the NMSSM, but can be a good
approximation when singlet mixing is very small\footnote{These
  corrections may be disabled in the SLHA file, as described in
  section \secref{sec:PoleMasses}.}.

 The corrections can then be used in the calculation of the Higgs
 masses, when appropriate settings are selected in the SLHA file. Note
 that even in the NMSSM the user miust make an important decision as
 to whether or not to enable the generated MSSM corrections which are
 incomplete in the NMSSM.  We feel that it is valuable to have
 these MSSM corrections for scenarios where there singlet mixing is
 very small and in particular for cross checks against the MSSM when
 close to the MSSM limit of the model.  However in cases where the
 singlet mixing is large the result at $O(y_t^4 + y_t^2 y_b^2 +
 y_b^4)$ and $O(y_\tau^4)$ will not be complete and including these
 corrections could in principle even make the numerical result further
 away from the correct two loop result at that order if there is a
 cancellation with the missing contributions.  So while including such
 partial two-loop corrections does not change the formal accuracy
 the user should choose whether or not to include these corrections
 based on the physics they study.  Similarly in models that go beyond
 the NMSSM the user must decide based the physics whether on not these
 corrections will give the leading two-loop corrections in their
 model.

@@

Finally, with the variable \code{ExtraSLHAOutputBlocks} the user can
define extra SLHA output blocks.  The values of the block entries will
be calculated at the output scale, which is specified in entry $12$ in
the SLHA input block \code{MODSEL}.  In the example model file above
the following six extra SLHA compliant output blocks are defined:
\code{ALPHA}, \code{HMIX}, \code{Au}, \code{Ad}, \code{Ae} and
\code{MSOFT}.  The \code{ALPHA} output block contains the CP-even
Higgs pole mass mixing angle as the only entry.  The \code{HMIX}
output block contains the $\mu$-parameter, the ratio $\tan\beta =
v_u/v_d$, the combination $v=\sqrt{v_u^2 + v_d^2}$, the squared mass
of the CP-odd Higgs $m_A^2$, the soft-breaking parameter $B\mu$ and
the values of $v_u$ and $v_d$, all defined in the \DRbar\ scheme.  In
an analogue way four more output blocks for the soft-breaking \DRbar\
parameters are defined.  For a CMSSM example parameter point with $m_0
= 125\unit{GeV}$, $M_{1/2} = 500\unit{GeV}$, $\tan\beta = 10$,
$\sign\mu = +1$ and $A_0 = 0$ the \fs-generated CMSSM spectrum
generator writes the so defined blocks to the output in the form
%
\begin{lstlisting}
Block ALPHA Q= 8.76740936E+02
           1.06784138E-01   # ArcCos(Pole(ZH(0,1)))
Block HMIX Q= 8.76740936E+02
     1     6.31218384E+02   # Mu
     2     9.67312621E+00   # vu/vd
     3     2.44053433E+02   # Sqrt(Sqr(vd) + Sqr(vu))
     4     5.36777230E+05   # Sqr(MAh(1))
   101     5.49048159E+04   # BMu
   102     2.50962986E+01   # vd
   103     2.42759663E+02   # vu
Block Au Q= 8.76740936E+02
  1  1    -1.14477419E+03   # TYu(0,0)/Yu(0,0)
  2  2    -1.14476911E+03   # TYu(1,1)/Yu(1,1)
  3  3    -8.83902977E+02   # TYu(2,2)/Yu(2,2)
Block Ad Q= 8.76740936E+02
  1  1    -1.40026447E+03   # TYd(0,0)/Yd(0,0)
  2  2    -1.40025976E+03   # TYd(1,1)/Yd(1,1)
  3  3    -1.30885006E+03   # TYd(2,2)/Yd(2,2)
Block Ae Q= 8.76740936E+02
  1  1    -3.00005426E+02   # TYe(0,0)/Ye(0,0)
  2  2    -3.00000006E+02   # TYe(1,1)/Ye(1,1)
  3  3    -2.98364373E+02   # TYe(2,2)/Ye(2,2)
Block MSOFT Q= 8.76740936E+02
     1     2.09018579E+02   # MassB
     2     3.88257873E+02   # MassWB
     3     1.11544211E+03   # MassG
    21     1.09683411E+05   # mHd2
    22    -3.85898988E+05   # mHu2
    31     3.54416224E+02   # Sqrt(ml2(0,0))
    32     3.54412891E+02   # Sqrt(ml2(1,1))
    33     3.53407333E+02   # Sqrt(ml2(2,2))
    34     2.22035720E+02   # Sqrt(me2(0,0))
    35     2.22024873E+02   # Sqrt(me2(1,1))
    36     2.18731935E+02   # Sqrt(me2(2,2))
    41     1.02053367E+03   # Sqrt(mq2(0,0))
    42     1.02053107E+03   # Sqrt(mq2(1,1))
    43     9.40760849E+02   # Sqrt(mq2(2,2))
    44     9.82565930E+02   # Sqrt(mu2(0,0))
    45     9.82563167E+02   # Sqrt(mu2(1,1))
    46     8.09126982E+02   # Sqrt(mu2(2,2))
    47     9.77979392E+02   # Sqrt(md2(0,0))
    48     9.77976666E+02   # Sqrt(md2(1,1))
    49     9.73121951E+02   # Sqrt(md2(2,2))
\end{lstlisting}

@@

If, however, the different solutions are not related by global signs,
then \fs writes all solutions to the file
\code{models/<model>/<model>_tree_level_EWSB_solution.m}.  The user
has then the option to pick a particular solution by setting it in the
\code{TreeLevelEWSBSolution} variable in the model file.  This is for
example the case in the $Z_3$-violating NMSSM (\code{SMSSM}), which is shipped with \fs, where
$\mu$ is chosen to be fixed by the EWSB equations: There the
tree-level solution for $\mu$ has the form
%
\begin{align}
  \mu = -\frac{v_s \lambda}{\sqrt{2}} + \sign X \cdot \sqrt{\ldots}
\end{align}
%
with $\sign X$ as free parameter.  When \fs solves the tree-level EWSB
equations for $\mu$, $B\mu$ and $\xi_S$ it finds the two solutions and
writes them to \code{models/SMSSM/SMSSM_tree_level_EWSB_solution.m} in
the form
%
\begin{lstlisting}[language=Mathematica]
{
   {{B[\[Mu]] -> ...}},
   {
      {\[Mu] -> (-20*Sqrt[2]*vd*vS*(\[Lambda] + conj[\[Lambda]])
                 - Sqrt[...])/(80*vd)},
      {\[Mu] -> (-20*Sqrt[2]*vd*vS*(\[Lambda] + conj[\[Lambda]])
                 + Sqrt[...])/(80*vd)}
   },
   {{L[L1] -> ...}}
}
\end{lstlisting}
%
In the above solutions the dots stand for the full expression, which
is left out here for better readability.  Inspecting the two above
solutions for $\mu$, one finds that both can be parametrized by an
additional free sign in front of the \code{Sqrt[...]}.  The user can
now introduce an additional free sign by hand in the \code{MINPAR}
block
%
\begin{lstlisting}[language=Mathematica]
MINPAR = {
   {1, m0},
   {2, m12},
   {3, TanBeta},
   {4, Sign[X]},  (* <-- additional free sign *)
   {5, Azero}
};
\end{lstlisting}
%
and set the the tree-level solution, parametrized in terms of
\code{Sign[X]}, in the \code{TreeLevelEWSBSolution} variable in
the model file:
%
\begin{lstlisting}
TreeLevelEWSBSolution = {
   { B[\[Mu]], ... },
   { \[Mu], (-20*Sqrt[2]*vd*vS*(\[Lambda] + conj[\[Lambda]])
             + Sign[X] * Sqrt[...])/(80*vd) },
   { L[L1], ... }
};
\end{lstlisting}
%
One can now chose between the two solutions by setting entry $4$ in
the \code{MINPAR} block of the SLHA input file to either $+1$ or $-1$.
See \code{model_files/SMSSM/FlexibleSUSY.m.in} for a complete example
model file.  If the user decides to not pick a particular solution by
leaving the variable \code{TreeLevelEWSBSolution} empty, \fs tries to
find a solution to the tree-level EWSB equations numerically via an
iteration.  In this case, however, the user does not have the option
to chose between the different solutions.

@@

The three different pole mass calculation procedures work as follows:
%
\begin{itemize}
\item \code{LowPrecision}: This option provides the lowest precision
  but is also the fastest one.  Here the one-loop mass matrix
  $m_{f,1L}^\text{low}$ is calculated exactly once as
%
  \begin{align}
    \forall i,j: (m_{f,1L}^\text{low})_{ij} = (m_{f,1L}(p^2 = m_{f_i}
    m_{f_j}))_{ij} ,
  \end{align}
%
  where $m_{f_i}$ is the $i$th mass eigenvalue of the tree-level mass
  matrix $m_f$.  Afterwards, $m_{f,1L}^\text{low}$ is diagonalized and
  the eigenvalues are interpreted as pole masses $m_{f_i}^\pole$.
  This method neglects terms of the form
  %
  \begin{align}
    \left[(m_{f_k}^\pole)^2 - m_{f_i}m_{f_j}\right]
    \left.\frac{\partial m_{f,1L}(p^2)}{\partial
        p^2}\right|_{p^2=m_{f_i}m_{f_j}} ,
  \end{align}
  %
  which are formally of two-loop order.  The method is imprecise if
  the self-energy corrections to the mass matrix are large or the
  tree-level mass spectrum of the multiplet is very split.  Note: We
  strongly discourage the use of this method for the determination the
  Higgs pole masses, as the result will very imprecise due to the
  large loop corrections.  \fs will print a warning if this method is
  used for any Higgs boson.

@@

are small for this parameter point, it's pole mass varies only in the

@@

$\unit{0.4\%}$, one can consider calculating then with

@@

Since the Higgs mass is a very important measurement and the two-loop
corrections can be larger than the current experimental error
\cite{Degrassi:2009yq} we recommend to set these switches to
\code{True} in any MSSM-\footnote{In \fs a model is MSSM-like if (i)
  its superpotential is approximately given by the MSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains two $CP$-even and $CP$-odd Higgs bosons, where one $CP$-odd
  Higgs boson may be a Goldstone boson, all with an MSSM-like coupling
  to $t$, $b$ and $\tau$.} and NMSSM-like\footnote{In \fs a model is
  NMSSM-like if (i) its superpotential is approximately given by the
  NMSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains three $CP$-even and $CP$-odd Higgs
  bosons, where one or two $CP$-odd Higgs bosons may be Goldstone
  bosons, all with an NMSSM-like coupling to $t$, $b$ and $\tau$\@.
  Examples for NMSSM-like models are the USSM and the \ESSM.} model.
However in such models the user should still consider whether these
corrections are really the leading corrections in the model or if
there are other potentially large two-loop corrections which are
missing.  For models with a more extended Higgs sector we recommend
that the leading log two-loop corrections are estimated by
generalizing those of the MSSM or NMSSM.

@@

    \cite{Ellwanger:2009dp,Allanach:2013kza}.}

@@

The \fs generated NUHM \ESSM\ spectrum generator has also been
compared against a handwritten one for a constrained version of the
\ESSM \cite{Athron:2009ue, Athron:2009bs, Athron:2012pw}.  The
$\beta$-functions were systematically compared in unit tests and were
found to match within numerical precision.  The handwritten code
doesn't include full one-loop self-energies or tadpoles, so tests on
these were not carried out.  Although the generators assume different
constraints and solve the boundary value problem with completely
different algorithms they could be compared by using the output of
the CE$_6$SSM generator as an input to \fs and the spectra were found
to be in reasonable agreement  given the different levels of precision with deviatiuons in the mass spectra $\lesssim 10\%$.

>>>>

\subsection{Current limitations and future extensions}
Although we try to handle as many models as possible, there are still
some limitations to what can be done. In its current form \fs assumes
all couplings are real, therefore it is limited to $CP$-conserving
versions of SUSY models.  Although it is implicit in the title, we
would like to stress that currently we cannot provide a spectrum
generator for non-SUSY models.  This also means that like other
spectrum generators it is difficult to reliably predict the mass
spectrum in extreme cases such as Split-SUSY
\cite{Wells:2003tf,ArkaniHamed:2004fb,Giudice:2004tc}, where the mass
scales of the SUSY model are drastically split, leading to very large
logarithms which are not resummed.  In such cases the tower of
effective theories offers the best possibility for a solution.
However, for this to work \fs must be extended to include non-SUSY
models.  Finally, the gauge group of the model is currently restricted
to be semi-simple and to contain the Standard Model gauge group as
factor, so that the SUSY model can be directly matched to the SM at
low energies.
%
Future releases which extend \fs beyond each of these limitations are
already planned.

@@

\fs allows the user to add leading two-loop contributions to the
$CP$-even and $CP$-odd Higgs self-energies as well as to the $CP$-even Higgs
tadpoles.  For MSSM-like models (with two $CP$-even Higgs bosons, one
$CP$-odd Higgs boson, one neutral Goldstone boson) routines for
calculating these corrections will be generated by setting
\code{UseHiggs2LoopMSSM = True} in the model file and by defining the
effective $\mu$-term \code{EffectiveMu = \\[Mu]}.  This will add the
zero-momentum corrections of the order $O(y_t^4 + y_b^2 y_t^2 +
y_b^4)$, $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$, $O(y_\tau^4)$ from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}.
For NMSSM-like models (with three $CP$-even Higgs bosons, two $CP$-odd
Higgs bosons, one neutral Goldstone boson) the two-loop contributions
are generated by setting \code{UseHiggs2LoopNMSSM = True} and by
defining the effective $\mu$-term like \code{EffectiveMu = \\[Lambda]
  vS / Sqrt[2]}, for example.  This will add the zero-momentum
corrections of the order $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ from
\cite{Degrassi:2009yq} and also the MSSM contributions of the order
$O(y_\tau^4)$, $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ as well
\cite{Brignole:2001jy,Dedes:2003km} which only represent a partial
correction for that order in the NMSSM, but can be a good
approximation when singlet mixing is very small\footnote{These
  corrections may be disabled in the SLHA file, as described in
  section \secref{sec:PoleMasses}.}.

 The corrections can then be used in the calculation of the Higgs
 masses, when appropriate settings are selected in the SLHA file. Note
 that even in the NMSSM the user must make an important decision as
 to whether or not to enable the generated MSSM corrections which are
 incomplete in the NMSSM.  We feel that it is valuable to have
 these MSSM corrections for scenarios where singlet mixing is
 very small and in particular for cross checks against the MSSM when
 close to the MSSM limit of the model.  However in cases where the
 singlet mixing is large the result at $O(y_t^4 + y_t^2 y_b^2 +
 y_b^4)$ and $O(y_\tau^4)$ will not be complete and including these
 corrections could in principle even make the numerical result further
 away from the correct two loop result at that order if there is a
 cancellation with the missing contributions.  So while including such
 partial two-loop corrections does not change the formal accuracy
 the user should choose whether or not to include these corrections
 based on the physics they study.  Similarly in models that go beyond
 the NMSSM the user must decide based the physics whether on not these
 corrections will give the leading two-loop corrections in their
 model.

@@

Finally, with the variable \code{ExtraSLHAOutputBlocks} the user can
define extra SLHA output blocks.  The values of the block entries will
be calculated at the output scale, which is specified in entry $12$ in
the SLHA input block \code{MODSEL}.  In the example model file above
the following six extra SLHA compliant output blocks are defined:
\code{ALPHA}, \code{HMIX}, \code{Au}, \code{Ad}, \code{Ae} and
\code{MSOFT}.  The \code{ALPHA} output block contains the CP-even
Higgs pole mass mixing angle as the only entry.  The \code{HMIX}
output block contains the $\mu$-parameter, the ratio $\tan\beta =
v_u/v_d$, the combination $v=\sqrt{v_u^2 + v_d^2}$, the squared mass
of the CP-odd Higgs $m_A^2$, the soft-breaking parameter $B\mu$ and
the values of $v_u$ and $v_d$, all defined in the \DRbar\ scheme.  In
an analogous way four more output blocks for the soft-breaking \DRbar\
parameters are defined.  For a CMSSM example parameter point with $m_0
= 125\unit{GeV}$, $M_{1/2} = 500\unit{GeV}$, $\tan\beta = 10$,
$\sign\mu = +1$ and $A_0 = 0$ the \fs-generated CMSSM spectrum
generator writes the so defined blocks to the output in the form
%
\begin{lstlisting}
Block ALPHA Q= 8.76740936E+02
           1.06784138E-01   # ArcCos(Pole(ZH(0,1)))
Block HMIX Q= 8.76740936E+02
     1     6.31218384E+02   # Mu
     2     9.67312621E+00   # vu/vd
     3     2.44053433E+02   # Sqrt(Sqr(vd) + Sqr(vu))
     4     5.36777230E+05   # Sqr(MAh(1))
   101     5.49048159E+04   # BMu
   102     2.50962986E+01   # vd
   103     2.42759663E+02   # vu
Block Au Q= 8.76740936E+02
  1  1    -1.14477419E+03   # TYu(0,0)/Yu(0,0)
  2  2    -1.14476911E+03   # TYu(1,1)/Yu(1,1)
  3  3    -8.83902977E+02   # TYu(2,2)/Yu(2,2)
Block Ad Q= 8.76740936E+02
  1  1    -1.40026447E+03   # TYd(0,0)/Yd(0,0)
  2  2    -1.40025976E+03   # TYd(1,1)/Yd(1,1)
  3  3    -1.30885006E+03   # TYd(2,2)/Yd(2,2)
Block Ae Q= 8.76740936E+02
  1  1    -3.00005426E+02   # TYe(0,0)/Ye(0,0)
  2  2    -3.00000006E+02   # TYe(1,1)/Ye(1,1)
  3  3    -2.98364373E+02   # TYe(2,2)/Ye(2,2)
Block MSOFT Q= 8.76740936E+02
     1     2.09018579E+02   # MassB
     2     3.88257873E+02   # MassWB
     3     1.11544211E+03   # MassG
    21     1.09683411E+05   # mHd2
    22    -3.85898988E+05   # mHu2
    31     3.54416224E+02   # Sqrt(ml2(0,0))
    32     3.54412891E+02   # Sqrt(ml2(1,1))
    33     3.53407333E+02   # Sqrt(ml2(2,2))
    34     2.22035720E+02   # Sqrt(me2(0,0))
    35     2.22024873E+02   # Sqrt(me2(1,1))
    36     2.18731935E+02   # Sqrt(me2(2,2))
    41     1.02053367E+03   # Sqrt(mq2(0,0))
    42     1.02053107E+03   # Sqrt(mq2(1,1))
    43     9.40760849E+02   # Sqrt(mq2(2,2))
    44     9.82565930E+02   # Sqrt(mu2(0,0))
    45     9.82563167E+02   # Sqrt(mu2(1,1))
    46     8.09126982E+02   # Sqrt(mu2(2,2))
    47     9.77979392E+02   # Sqrt(md2(0,0))
    48     9.77976666E+02   # Sqrt(md2(1,1))
    49     9.73121951E+02   # Sqrt(md2(2,2))
\end{lstlisting}

@@

If, however, the different solutions are not related by global signs,
then \fs writes all solutions to the file
\code{models/<model>/<model>_tree_level_EWSB_solution.m}.  The user
has then the option to pick a particular solution by setting it in the
\code{TreeLevelEWSBSolution} variable in the model file.  This is for
example the case in the $Z_3$-violating NMSSM (\code{SMSSM}), which is shipped with \fs, where
$\mu$ is chosen to be fixed by the EWSB equations: There the
tree-level solution for $\mu$ has the form
%
\begin{align}
  \mu = -\frac{v_s \lambda}{\sqrt{2}} + \sign X \cdot \sqrt{\ldots}
\end{align}
%
with $\sign X$ as free parameter.  When \fs solves the tree-level EWSB
equations for $\mu$, $B\mu$ and $\xi_S$ it finds the two solutions and
writes them to \code{models/SMSSM/SMSSM_tree_level_EWSB_solution.m} in
the form
%
\begin{lstlisting}[language=Mathematica]
{
   {{B[\[Mu]] -> ...}},
   {
      {\[Mu] -> (-20*Sqrt[2]*vd*vS*(\[Lambda] + conj[\[Lambda]])
                 - Sqrt[...])/(80*vd)},
      {\[Mu] -> (-20*Sqrt[2]*vd*vS*(\[Lambda] + conj[\[Lambda]])
                 + Sqrt[...])/(80*vd)}
   },
   {{L[L1] -> ...}}
}
\end{lstlisting}
%
In the above solutions the dots stand for the full expression, which
is left out here for better readability.  Inspecting the two above
solutions for $\mu$, one finds that both can be parametrized by an
additional free sign in front of the \code{Sqrt[...]}.  The user can
now introduce an additional free sign by hand in the \code{MINPAR}
block
%
\begin{lstlisting}[language=Mathematica]
MINPAR = {
   {1, m0},
   {2, m12},
   {3, TanBeta},
   {4, Sign[X]},  (* <-- additional free sign *)
   {5, Azero}
};
\end{lstlisting}
%
and set the the tree-level solution, parametrized in terms of
\code{Sign[X]}, in the \code{TreeLevelEWSBSolution} variable in
the model file:
%
\begin{lstlisting}
TreeLevelEWSBSolution = {
   { B[\[Mu]], ... },
   { \[Mu], (-20*Sqrt[2]*vd*vS*(\[Lambda] + conj[\[Lambda]])
             + Sign[X] * Sqrt[...])/(80*vd) },
   { L[L1], ... }
};
\end{lstlisting}
%
One can now choose between the two solutions by setting entry $4$ in
the \code{MINPAR} block of the SLHA input file to either $+1$ or $-1$.
See \code{model_files/SMSSM/FlexibleSUSY.m.in} for a complete example
model file.  If the user decides to not pick a particular solution by
leaving the variable \code{TreeLevelEWSBSolution} empty, \fs tries to
find a solution to the tree-level EWSB equations numerically via an
iteration.  In this case, however, the user does not have the option
to choose between the different solutions.

@@

The three different pole mass calculation procedures work as follows:
%
\begin{itemize}
\item \code{LowPrecision}: This option provides the lowest precision
  but is also the fastest one.  Here the one-loop mass matrix
  $m_{f,1L}^\text{low}$ is calculated exactly once as
%
  \begin{align}
    \forall i,j: (m_{f,1L}^\text{low})_{ij} = (m_{f,1L}(p^2 = m_{f_i}
    m_{f_j}))_{ij} ,
  \end{align}
%
  where $m_{f_i}$ is the $i$th mass eigenvalue of the tree-level mass
  matrix $m_f$.  Afterwards, $m_{f,1L}^\text{low}$ is diagonalized and
  the eigenvalues are interpreted as pole masses $m_{f_i}^\pole$.
  This method neglects terms of the form
  %
  \begin{align}
    \left[(m_{f_k}^\pole)^2 - m_{f_i}m_{f_j}\right]
    \left.\frac{\partial m_{f,1L}(p^2)}{\partial
        p^2}\right|_{p^2=m_{f_i}m_{f_j}} ,
  \end{align}
  %
  which are formally of two-loop order.  The method is imprecise if
  the self-energy corrections to the mass matrix are large or the
  tree-level mass spectrum of the multiplet is very split.  Note: We
  strongly discourage the use of this method for the determination of the
  Higgs pole masses, as the result will be very imprecise due to the
  large loop corrections.  \fs will print a warning if this method is
  used for any Higgs boson.

@@

are small for this parameter point, its pole mass varies only in the

@@

$\unit{0.4\%}$, one can consider calculating them with

@@

Since the Higgs mass is a very important measurement and the two-loop
corrections can be larger than the current experimental error
\cite{Degrassi:2009yq} we recommend to set these switches to
\code{True} in any MSSM-\footnote{In \fs a model is MSSM-like if (i)
  its superpotential is approximately given by the MSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains two $CP$-even and $CP$-odd Higgs bosons, where one $CP$-odd
  Higgs boson may be a Goldstone boson, all with an MSSM-like coupling
  to $t$, $b$ and $\tau$.} and NMSSM-like\footnote{In \fs a model is
  NMSSM-like if (i) its superpotential is approximately given by the
  NMSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains three $CP$-even and $CP$-odd Higgs
  bosons, where one or two $CP$-odd Higgs bosons may be Goldstone
  bosons, all with an NMSSM-like coupling to $t$, $b$ and $\tau$\@.
  Examples for NMSSM-like models are the USSM and the \ESSM.} model.
However in such models the user should still consider whether these
corrections are really the leading corrections in the model or %if
there are other potentially large two-loop corrections which are
missing.  For models with a more extended Higgs sector we recommend
that the leading log two-loop corrections are estimated by
generalizing those of the MSSM or NMSSM.

@@

    \cite{Allanach:2013kza,Ellwanger:2009dp}.}

@@

The \fs generated NUHM \ESSM\ spectrum generator has also been
compared against a handwritten one for a constrained version of the
\ESSM \cite{Athron:2009ue, Athron:2009bs, Athron:2012pw}.  The
$\beta$-functions were systematically compared in unit tests and were
found to match within numerical precision.  The handwritten code
doesn't include full one-loop self-energies or tadpoles, so tests on
these were not carried out.  Although the generators assume different
constraints and solve the boundary value problem with completely
different algorithms they could be compared by using the output of
the CE$_6$SSM generator as an input to \fs and the spectra were found
to be in reasonable agreement  given the different levels of precision with deviations in the mass spectra $\lesssim 10\%$.
